Allee Effect and Cultural Evolution

### 2015-06-03 manuscript/draft.tex
updated lambda equations
Update

Equation \eqref{eq2} depicts the so called \emph{strong} Allee effect \citep{Wang_and_Kot_2001}, where the reproductive rate is negative when population density is either below $A$ or above $K$, and  in this case reach its maxima $R_{max}=\frac{r(A-K)2}{4AK}$ when density is equal to $\frac{(K-A)}{2}$.

@@

@@

@@

The analyses of the previous section suggest that maximum proportion of population that can switch strategies (i.e. the $z$ parameter) has major effects on the final equilibria (c.f. fig.\ref{fig:bifurcationWithTransmission}). However, this will also depend on the key parameters defining the range of positive payoff for the two strategies (i.e. $[A_a,K_a]$ and $[A_b,K_b]$). While a comprehensive analysis is not possible, here we illustrate the relationship between these parameters and $z$ by introducing a new parameter $\lambda \in (0,1)$ adding the following constraints to equation \eqref{eq1}: 
%I slightly revised your intro here. Mainly because this reads as if changes depends on the intervals of positive payoff alone, while I think it actually depends on any possibly combination of values. 
\begin{equation}
\begin{aligned}
\label{eqOverlap}
A_b = A_a + \lambda A_a\\
K_b = K_a + \lambda K_a
\end{aligned}
\end{equation}

%ENRICO:
%I'm a bit confused by \eqref{eqOverlap}. Clearly lambda is no longer a measure of overlap percentage, as when lambda=0 we have identical strategy, but when lambda=1 we can have a variety of patterns depending on what you have at A_a and K_a. For example if you have A_a=3 and K_a=5, you will get A_b=6 and K_b=10, thus no overlap between the two strategies. But if you have A_a=1 and K_a=5, then you will have A_b=2, and K_b=10 which implies an almost complete overlap. Besides this approach does not hold the differences constant. I thought you did:

% \begin{equation}
%\begin{aligned}
%\label{eqOverlap}
%A_b = A_a + (1-\lambda A_a)(K_a-A_a)\\
%K_b = K_a + (1-\lambda A_a)(K_a-A_a)
%\end{aligned}
% \end{equation}

%which would instead give, with lambda=0 this time, A_a=3 K_a=5 A_b=5, K_b=7 for the first example, and  A_a=1 K_a=5 A_b=5, K_b=9 for the second.

@@

%Ok this reads more like my interpretation of lambda..

>>>>

Equation \eqref{eq2} depicts the so called \emph{strong} Allee effect \citep{Wang_and_Kot_2001}, where the reproductive rate is negative when population density is either below $A$ or above $K$, and  in this case reach its maxima $R_{max}=\frac{r(A-K)^2}{4AK}$ when density is equal to $\frac{(K-A)}{2}$.

%Check if $R_{max}=\frac{r(A-K)^2}{4AK}$ this actually true, or is rather $R_{max}=\frac{r(K-A)2}{4AK}$

@@

%This should be changed with the basin plot and the time-series; omit discussion on bifurcation

@@

Small differences in initial conditions can have major consequences in the boundaries between the unstable region and the rest of equilibria. Figure \ref{fig:unstable} shows an example with high value of social learning $z=0.4$, where two scenarios ($j$ and $k$) generate different outcomes from very close initial conditions.

@@

The analyses of the previous section suggest that maximum proportion of population that can switch strategies (i.e. the $z$ parameter) has major effects on the final equilibria (c.f. fig.\ref{fig:bifurcationWithTransmission}). However, this will also depend on the key parameters defining the range of positive payoff for the two strategies (i.e. $[A_a,K_a]$ and $[A_b,K_b]$). While a comprehensive analysis is not possible, here we illustrate the relationship between these parameters and $z$ by introducing a new parameter $\lambda \in (0,1)$ adding the following constraints to equation \eqref{eq1}: 
%I slightly revised your intro here. Mainly because this reads as if changes depends on the intervals of positive payoff alone, while I think it actually depends on any possibly combination of values.

\begin{equation}
\begin{aligned}
\label{eqOverlap}
A_b = A_a + (1-\lambda)(K_a-A_a)\\
K_b = K_a + (1-\lambda)(K_a-A_a)
\end{aligned}
\end{equation}

@@
